Multi-Agent Path Finding with Matching using Increasing Cost Tree Search

### 2021-06-07 docs/paper.tex
Fixed some issues using grammarly

	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
	Such methods are suboptimal and heuristic solutions to instances defined for a set shunting yard can be said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost. 
	The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion. 
	Mulderij et al. \cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation for finding such upper-bounds using an approach analogous to that outlined above.
	For this to succeed, a way to optimally solve MAPFM instances is needed.

	Comparatively, little research has been done on MAPFM and solving MAPFM optimally.
	The Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}.
	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search. It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CMB are needed in order to minimize SIC.
	The successful application of CBS to solving MAPFM begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?

	\begin{wrapfigure}{R}{.25\textwidth}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Swapping conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\caption{The two types of conflict (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
	\end{wrapfigure}
	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}. ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path costs and a bottom-level evaluation of ICT nodes using multi-valued decision diagrams (MDDS). These MDDS represent per agent all possible paths to the goal of a set length. In the context of a research project in which multiple such 
	MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}. In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}.Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.

@@

	So given a combination of paths $(\pi_1,\ldots,\pi_k)$, a vector of costs is found from which the SIC is derived. This is a surjective mapping: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$. On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up search. In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
	\subsection{Increasing Cost Tree Search}
	\label{icts}
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.4\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
		\label{fig:symmetries}
	\end{figure}
	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to SIC is reversed in order to search for a solution with minimal SIC. This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.

@@

	\caption{Example of using ICTS to solve MAPF from \cite{sharon2011}}
	\label{fig:bottom}
\end{figure}
	\subsubsection{Bottom-level search}
	Explicitly generating all paths to the goal for agent $a_i$ of cost $c_i$ is expensive: the number of paths is exponential in $c_i$. This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent. For $a_i$ with target cost $c_i$ (from cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents. Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations.

	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as low-level search of the (solution) node $(3,2)$ using MDDs. Note that the second agent staying at node D after completing the path is modelled in its MDD also to ensure that place remains blocked.

	Subfigure \ref{fig:mdds} illustrates the way in which two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts. In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD. If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would similarly be a swapping conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$. In the next layer, the process repeats with multiple parent nodes.

	In practice, joint MDDs are not explicitly constructed but instead a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
	\subsubsection{ICTS with Independence Detection}
	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.
	\begin{algorithm}
	\begin{algorithmic}[1]
		\State \text{Assign each agent to a singleton group}
		\State \text{plan a path for each group}
		\Repeat
			\State \text{simulate execution of all paths until a conflict occurs}
			\State \text{merge two conflicting groups into a single group}
			\State \text{cooperatively plan new group}
		\Until{\text{no conflicts occur}}
		\State $solution\gets\text{paths of all groups combined}$
		\State \textbf{return solution}
	\end{algorithmic}
	\caption{Simple Independence Detection by Standley} 
	\label{id-algo}
	\end{algorithm}

@@

	As a further improvement of this method, the order in which matchings are enumerated and solved could be changed. In particular, by sorting the matchings in increasing order of root SIC, it can be seen that $\Delta'_{m + 1}$, the distance from $B_{m+1}$ or the solution to matching $m + 1$ (whichever was reached first) and the root SIC, will always be less or equal to the $\Delta'_m$ [TODO: proof]. Although this is itself a promising property, in order to make use of it, all roots have to be computed and all $M$ corresponding SIC values have to be sorted which is a $\mathcal{O}(M\log M)$ procedure.

	\subsection{ICTS-m}
	ICTS with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances. Few changes to ICTS were necessary to accomodate for matching in this increasing cost tree scheme. Specifically, the ICT root generation and the MDD generation had to be changed. As described in \ref{icts}, in ICTS the root cost for each agent $a_i$ is given by $c^*_i$, the cost of the shortest path from $s_i$ to $g_i$, i.e. without taking conflicts into account. $MDD_i^{c_i}$ is generated using a breadth-first search from $s_i$ to $g_i$ followed by some additional processing.
	\subsubsection{Root generation for matching}
	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$. Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{0,\ldots,k_i\}} c_j(n)$. Therefore, to guarantee optimality, this minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root. The resulting root is equivalent to that generated in regular ICTS in the case that all teams are singleton, which is equivalent to a MAPF instance. Intuitively, the sum of individual costs of this root is highly optimistic, in particular if the teams are large. This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.

	\subsubsection{MDD generation for matching}
	In MDD generation, each agent also has to consider not one goal but all matching goals. By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD was generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal. Once again, if all teams are singleton, the MDDs generated using this goal-set approach are the same as in regular ICTS.
	\begin{wrapfigure}{R}{.35\textwidth}
	\centering
	\includegraphics[width=\linewidth]{img/path}
	\caption{Pathelogical case for ICTS-m [Placeholder graphic]}
	\label{fig:path}
\end{wrapfigure}
	\subsubsection{Properties of ICTS-m}
As a consequence of the $\min$ operation in the root definition, a pathelogical case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. As indicated by the color, all four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is, numbering the agents clockwise, $(1,3,3,3)$ with SIC $10$, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	\subsection{General optimization: child pruning}
An optimization of ICTS that hitherto appears to not have been described in the literature was found in the process of optimizing ICTS-m. The idea is simple: when pruning, in the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation. However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented in any solution node. This reduces the number of children generated to the number of conflicting agents, which quite drastically can improve the branching factor of the ICT search if say $k = 12$ but a conflicting pair is found.

>>>>

	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
	Such methods are suboptimal and heuristic solutions to instances defined for a set shunting yard can be said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper bound for the optimal solution cost. 
	The railway company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about matters like infrastructure expansion. 
	Mulderij et al. \cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation for finding such upper-bounds using an approach analogous to that outlined above.
	For this to succeed, a way to optimally solve MAPFM instances is needed.

	Comparatively, little research has been done on MAPFM and solving MAPFM optimally.
	The Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} is one of the few existing approaches to optimally solve this more general problem along with the somewhat similar one described in \cite{henkel2019}.
	Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework, while exploiting the connection between MAPF problems and max-flow problems (as discussed in \cite{yu2013}) in the low-level search. It should be noted that this method minimizes the makespan and not the sum of individual costs which is the objective used in the TUSS relaxation, meaning that non-trivial modifications to CMB are needed to minimize SIC.
	The successful application of CBS to solving MAPFM begs the question: can alternative MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} also serve as the basis for a MAPFM solver?

	\begin{wrapfigure}{R}{.25\textwidth}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Swapping conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\caption{The two types of conflict (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
	\end{wrapfigure}
	This work is the outcome of a search for an efficient algorithm for optimally solving MAPFM derived from ICTS as an alternative to the approach outlined above\footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}. ICTS, in short, is a two-level approach to MAPF with a top-level breadth-first traversal of an Increasing Cost Tree (ICT) representing combinations of per-agent path costs and a bottom-level evaluation of ICT nodes using multi-valued decision diagrams (MDDS). These MDDS represent per agent all possible paths to the goal of a set length. In the context of a research project in which multiple such 
	MAPF algorithms were taken as starting points for MAPFM algorithms within a group, the novel ICTS-based algorithm is compared to these algorithms on a set of benchmarks similar to those described in \cite{stern2019}. In addition, it is analysed in terms of complexity and compared to both an enumerative approach that solves all matchings using regular ICTS and the algorithm described in \cite{ma2016}. Regarding the relevance of this work, it should be noted that besides TUSS, there are other applications such as planning warehouse robots \cite{wurman2007} that also could benefit from novel algorithms for MAPFM.

@@

	So given a combination of paths $(\pi_1,\ldots,\pi_k)$, a vector of costs is found from which the SIC is derived. This is a surjective mapping: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$. On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods like Jump Point Search\cite{harabor2011} are used to speed up the search. In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
	\subsection{Increasing Cost Tree Search}
	\label{icts}
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.4\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
		\label{fig:symmetries}
	\end{figure}
	In Increasing Cost Tree Search\cite{sharon2011}, the above two-step mapping from path combination to SIC is reversed to search for a solution with minimal SIC. This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.

@@

		\caption{Example of using ICTS to solve MAPF from \cite{sharon2011}}
		\label{fig:bottom}
	\end{figure}
	\subsubsection{Bottom-level search}
	Explicitly generating all paths to the goal for agent $a_i$ of cost $c_i$ is expensive: the number of paths is exponential in $c_i$. This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent. For $a_i$ with a target cost $c_i$ (from cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents. Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations.

	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs. Note that the second agent staying at node D after completing the path is modelled in its MDD also to ensure that the place remains blocked.

	Subfigure \ref{fig:mdds} illustrates how two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts. In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD. If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would similarly be a swapping conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$. In the next layer, the process repeats with multiple parent nodes.

	In practice, joint MDDs are not explicitly constructed but instead, a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
	\subsubsection{ICTS with Independence Detection}
	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case, ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during the planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.
	\begin{algorithm}
		\begin{algorithmic}[1]
			\State \text{Assign each agent to a singleton group}
			\State \text{plan a path for each group}
			\Repeat
			\State \text{simulate execution of all paths until a conflict occurs}
			\State \text{merge two conflicting groups into a single group}
			\State \text{cooperatively plan new group}
			\Until{\text{no conflicts occur}}
			\State $solution\gets\text{paths of all groups combined}$
			\State \textbf{return solution}
		\end{algorithmic}
		\caption{Simple Independence Detection by Standley} 
		\label{id-algo}
	\end{algorithm}

@@

	As a further improvement of this method, the order in which matchings are enumerated and solved could be changed. In particular, by sorting the matchings in increasing order of root SIC, it can be seen that $\Delta'_{m + 1}$, the distance from $B_{m+1}$ or the solution to matching $m + 1$ (whichever was reached first) and the root SIC, will always be less or equal to the $\Delta'_m$ [TODO: proof]. Although this is itself a promising property, to make use of it, all roots have to be computed and all $M$ corresponding SIC values have to be sorted which is a $\mathcal{O}(M\log M)$ procedure.

	\subsection{ICTS-m}
	ICTS with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances. Few changes to ICTS were necessary to accommodate for matching in this increasing cost tree scheme. Specifically, the ICT root generation and the MDD generation had to be changed. As described in \ref{icts}, in ICTS the root cost for each agent $a_i$ is given by $c^*_i$, the cost of the shortest path from $s_i$ to $g_i$, i.e. without taking conflicts into account. $MDD_i^{c_i}$ is generated using a breadth-first search from $s_i$ to $g_i$ followed by some additional processing.
	\subsubsection{Root generation for matching}
	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$. Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{0,\ldots,k_i\}} c_j(n)$. Therefore, to guarantee optimality, this minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root. The resulting root is equivalent to that generated in regular ICTS in the case that all teams are singleton, which is equivalent to a MAPF instance. Intuitively, the sum of individual costs of this root is highly optimistic, in particular, if the teams are large. This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts.

	\subsubsection{MDD generation for matching}
	In MDD generation, each agent also has to consider not one goal but all matching goals. By following a BFS-based approach, with all team goals being goals in the search and in turn endpoints from which, using the time-expanded graph, the MDD was generated that is used in the low-level search, agent MDDs can be made to represent all possible paths of a set length to any matching goal. Once again, if all teams are singleton, the MDDs generated using this goal-set approach are the same as in regular ICTS.
	\begin{wrapfigure}{R}{.35\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/path}
		\caption{Pathelogical case for ICTS-m [Placeholder graphic]}
		\label{fig:path}
	\end{wrapfigure}
	\subsubsection{Properties of ICTS-m}
	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. As indicated by the color, all four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is, numbering the agents clockwise, $(1,3,3,3)$ with SIC $10$, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	\subsection{General optimization: child pruning}
	An optimization of ICTS that hitherto appears to not have been described in the literature was found in the process of optimizing ICTS-m. The idea is simple: when pruning, in the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation. However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented in any solution node. This reduces the number of children generated to the number of conflicting agents, which quite drastically can improve the branching factor of the ICT search if say $k = 12$ but a conflicting pair is found.
